\texttt{thornado}-transport: IMEX schemes for two-moment neutrino transport respecting Fermi-Dirac statistics

### 2019-03-30 Documents/M1/Astronum_2018/sections/TwoMoments.tex
Work on Astronum paper.

\subsection{Transport Equations}
\modified{We consider neutrino transport through a static background in a non-relativistic framework.  
For simplicity, we only include neutrino-matter interactions due to emission, absorption, and isoenergetic scattering.  
It is possible to include other interactions, such as neutrino-electron scattering and pair processes, in the two-moment model.  
However, these interactions result in dense coupling across neutrino energies and across neutrino species, and we have not yet considered the realizability-preserving property of our scheme in this case.
We leave this for future work.}

>>>>

\subsection{Transport Equations}
\modified{We consider neutrino transport through a static background in a non-relativistic framework.  
For simplicity, we only include neutrino--matter interactions due to emission, absorption, and isoenergetic scattering.  
It is possible to include other interactions, such as neutrino--electron scattering and pair processes, in the two-moment model.  
However, these interactions result in dense coupling across neutrino energies and across neutrino species, and we have not yet considered the realizability-preserving property of our scheme in this case.
We leave this for future work.}
